Everything you wanted to know about PanDA but were truly truly afraid to ask

### 2017-03-11 paper.tex
Ongoing section V
Stud: connection V to VI
Clean up

\usepackage{listings}
\usepackage{comment}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

@@

% ----------------------------------------------------------------------------
% ABSTRACT
% ----------------------------------------------------------------------------
\begin{abstract}
Experiments at the Large Hadron Collider (LHC) face unprecedented computing
challenges. Heterogeneous resources are distributed worldwide, thousands of
physicists analyzing the data need remote access to hundreds of computing
sites, the volume of processed data is beyond the exabyte scale, and data
processing requires more than billions of hours of computing usage per year. The
PanDA (Production and Distributed Analysis) system was developed to meet the
scale and complexity of LHC distributed computing for the ATLAS experiment. In
the process, the old batch job paradigm of computing in HEP was discarded in
favor of a far more flexible and scalable model. The success of PanDA at the LHC
is leading to widespread adoption and testing by other experiments. PanDA is
the first exascale workload management system in HEP, already operating at
a million computing jobs per day, and processing over an exabyte of data in
2013. We will describe the design and implementation of PanDA, present data on
the performance of PanDA at the LHC, and discuss plans for future evolution
of the system to meet new challenges of scale, heterogeneity and increasing
user base.
\end{abstract}

@@

% ----------------------------------------------------------------------------
% I - INTRODUCTION
% ----------------------------------------------------------------------------
\input{introduction}

\begin{enumerate}
  \item Problem that has been solved: executing many applications on
  heterogeneous distributed resources.
  \item Why are WMS needed?
  \item Increasing importance of WMS w.r.t complex and scalable applications on
  heterogeneous distributed resources.
  \item \ldots
  \item Overview/Summary of paper.
\end{enumerate}

@@

\begin{enumerate}
  \item Brief overview of distributed CI\@.
  \item Workload vs Workflow. (DONE)
  \item Distinguish between WFMS and WLMS\@.
  \begin{enumerate}
    \item Role of Workload MS\@: help ``hide'' and federate heterogeneous resources.
  \end{enumerate}
\end{enumerate}

% Please do not correct bckground to background.
\input{bckground}

\begin{enumerate}
  \item Other workload management systems (WMS) (not exclusive)
  \begin{enumerate}
    \item glidein-WMS
    \item Dirac
    \item ALICE-AlieN
  \end{enumerate}
  \begin{enumerate}
    \item Comparison and contrast
    \item Core features of a general WMS, i.e., minimal complete model of a WMS\@.
  \end{enumerate}
\end{enumerate}

\input{WMSLiterature}

@@

% \begin{enumerate}
%   \item Why? To support a specific stage of the ATLAS Monte Carlo Workflow.
%   \item Challenges
%   \item Opportunities
%   \item Highlight distinction of PanDA on wide-area distributed systems vs on TITAN
%   \item Take-aways, lessons learned
% \end{enumerate}

@@

% ----------------------------------------------------------------------------
% VI - PERFORMANCE CHARACTERIZATION
% ----------------------------------------------------------------------------
\section{Performance Characterization}
\label{sec:panda_titan}

@@

%\section{Putting it all together: Experience of PanDA on TITAN} % (fold)
%\label{sec:panda_titan}
%
%\begin{enumerate}
%  \item Metadata performance issue, and how it’s resolved
%  \item File I/O performance and impact
%  \item ?
%\end{enumerate}

@@

\begin{enumerate}
    \item Discussion of the limitations of the current state of the art
    \item Rationale and design (why)
    \item Architecture (how)
    \item Integration
    \item Characterization (experiments)
\end{enumerate}

\input{Experiments}

% ----------------------------------------------------------------------------
% VIII - CONCLUSIONS
% ----------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

The PanDA  system was developed to meet the scale and complexity of LHC
distributed computing for the ATLAS experiment.  In the process,  the old batch
job paradigm  of computing in HEP was  discarded  in favor of a  far more
flexible and scalable  model. The success  of PanDA  at the LHC is leading to
widespread adoption and testing by other experiments. PanDA  is the first
exascale  workload management system in HEP, already operating at a million
computing jobs per day, and processing over an exabyte of data in 2013. Next LHC
run will pose massive computing  challenges. With a  doubling of the beam
energy  and luminosity as  well as an increased  need for  simulates  data, the
data volume is expected to increase with a factor 5--6 or more. Storing and
processing  this amount of data is a  challenge   that cannot be resolved with
the currently existing  computing  resources in ATLAS\@. To resolve this
challenge, ATLAS is turning to commercial  as well as academic Cloud services
and HPCs via the PanDA system. Also the work underway is enabling the use of
PanDA by new scientific collaborations and communities as a means  of leveraging
extreme scale computing  resources with a low barrier of entry. The technology
base provided by the PanDA system will enhance the usage of a variety  of
high-performance computing resources available to basic research.

% ----------------------------------------------------------------------------
% ACKNOWLEDGEMENTS
% ----------------------------------------------------------------------------
\input{ack}

%\section*{Acknowledgment}

%The authors would like to thank... More thanks here...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

>>>>

@@

% ----------------------------------------------------------------------------
% ABSTRACT
% ----------------------------------------------------------------------------
\begin{abstract}
\input{abstract}
\end{abstract}

@@

% ----------------------------------------------------------------------------
% I - INTRODUCTION
% ----------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}

\input{introduction}

@@

\input{WMSLiterature}
% Please do not correct bckground to background.
\input{bckground}

@@

@@

% ----------------------------------------------------------------------------
% V - ANALYSIS AND DISCUSSION
% ----------------------------------------------------------------------------
\section{Analysis and Discussion}
\label{sec:panda_titan}

@@

@@

\input{nge}
\input{Experiments}

% ----------------------------------------------------------------------------
% VIII - CONCLUSION
% ----------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

\input{conclusion}

% ----------------------------------------------------------------------------
% ACKNOWLEDGEMENTS
% ----------------------------------------------------------------------------
\section*{Acknowledgements}
\label{sec:ack}

\input{ack}
